Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-03-30 ms.qmd
New doc, trying flextable which does formatting well, but still cross ref problems

---
title: "Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change"
bibliography: ./bib/refs.bib
csl: ./bib/ecology-letters.csl
format:
  docx:
    reference-doc: ./bib/template.docx
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto  # re-render only when source changes
  cache: true
  echo: false
  warning: false
  error: false
  include: true
crossref:
  fig-title: 'Figure'
  fig-labels: arabic
  title-delim: "-"
  fig-prefix: "Figure"
  tbl-prefix: "Table"
---

@@

### *Do terrestrial and aquatic ectotherms differ in their capacity to acclimate?*

@@

```
### *Does the opportunity for selection differ across terrestrial and aquatic ectotherms?*

@@

    slope_f_4.9 <- posteriors4.9[,"b_cv_c"]; mean(slope_f_4.9); pmcmc(slope_f_4.9); quantile(slope_f_4.9, c(0.025, 0.975))
    slope_m_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatm"]; mean(slope_m_4.9); pmcmc(slope_m_4.9); quantile(slope_m_4.9, c(0.025, 0.975))
    slope_t_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatt"]; mean(slope_t_4.9); pmcmc(slope_t_4.9); quantile(slope_t_4.9, c(0.025, 0.975))
```

### *Does climate variability predict acclimation capacity among aquatic and terrestrial ectotherms?*

@@

```{r}
#| label: tbl-tabs1
#| echo: false
#| tbl-cap: Model estimates, standard error, and 95% credible intervals comparing changes in acute and acclimation $lnVR_{Q_{10}}$ across habitat types. Models estimates are based off `r summary(model3.2_bayes)$nobs` effect sizes from `r summary(model3.2_bayes)$ngrps$record_num` studies.

@@

# Create the table
    tabs1 <- rbind(fixed, random)
   tabs1_2 <-  gt(tabs1) %>%  
    fmt_number(columns = 2:5, decimals = 2) %>% 
    tab_row_group(label = "Fixed Effects", rows = 1:7) %>% 
    tab_row_group(label = "Random Effects", rows = 8:11) %>%  
    tab_style(style = list(cell_text(weight = "bold")),
          locations = list(cells_column_labels(), cells_row_groups())) %>% 
    opt_table_lines(extent = "none")  %>% 
    tab_style(style = cell_borders(sides = c("top", "bottom")),
          locations = list(cells_column_labels()))  %>% 
    tab_style(style = cell_borders(sides = "bottom", weight = px(2)),
          locations =  cells_body(rows = 7))
    tabs1_2
```

@@

```{r, pubias}
#| label: pubias
#| echo: false

>>>>

---
title: "Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change"
bibliography: ./bib/refs.bib
csl: ./bib/ecology-letters.csl
format:
  docx:
    reference-doc: ./bib/template.docx
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto  # re-render only when source changes
  cache: false
  echo: false
  warning: false
  error: false
  include: true
crossref:
  fig-title: 'Figure'
  fig-labels: arabic
  title-delim: "-"
  fig-prefix: "Figure"
  tbl-prefix: "Table"
---

@@

### *Terrestrial and aquatic ectotherms differ in their capacity to acclimate but acclimation does not depend on life-history stage*

@@

```
### *The opportunity for selection is reduced in terrestrial ectotherms*

@@

    slope_f_4.9 <- posteriors4.9[,"b_cv_c"]; mean(slope_f_4.9); pmcmc(slope_f_4.9); quantile(slope_f_4.9, c(0.025, 0.975))
    slope_m_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatm"]; mean(slope_m_4.9); pmcmc(slope_m_4.9); quantile(slope_m_4.9, c(0.025, 0.975))
    slope_t_4.9 <- posteriors4.9[,"b_cv_c"] + posteriors4.9[,"b_cv_c:habitatt"]; mean(slope_t_4.9); pmcmc(slope_t_4.9); quantile(slope_t_4.9, c(0.025, 0.975))

### *Climate variability predicts acclimation capacity for terrestrial ectotherms*

@@

```{r}
#| label: tbl-tabs1
#| echo: false
#| tbl-cap: Model estimates, standard error, and 95% credible intervals comparing changes in acute and acclimation $lnVR_{Q_{10}}$ across habitat types. Models estimates are based off 1253 effect sizes from 139 studies.

@@

# Create the table
    tabs1 <- rbind(fixed, random)
   tabs1_2 <-  gt(tabs1) %>%  
    fmt_number(columns = 2:5, decimals = 2) %>% 
    tab_row_group(label = "Fixed Effects", rows = 1:7) %>% 
    tab_row_group(label = "Random Effects", rows = 8:11) %>%  
    tab_style(style = list(cell_text(weight = "bold")),
          locations = list(cells_column_labels(), cells_row_groups())) %>% 
    opt_table_lines(extent = "none")  %>% 
    tab_style(style = cell_borders(sides = c("top", "bottom")),
          locations = list(cells_column_labels()))  %>% 
    tab_style(style = cell_borders(sides = "bottom", weight = px(2)),
          locations =  cells_body(rows = 7))
    #tabs1_2

    flextable(tabs1)  %>%  autofit()
```

@@

```{r, pubias}
#| label: pubias
#| echo: false
#| include: false
